Discovering Focused Microgenre Communities: Toy example

### 2023-08-02 07-new-micro-analysis-for-real.Rmd
deleted plots and new plots

```{r}
    source(here("Functions", "micro.genre.dat.R"))
    source(here("Functions", "demog.dat.R"))
    source(here("Functions", "genre.reg.mods.R"))
    a <- demog.dat()
    summary(a)
    spec <- c("educ", "parcoll", "age.n", "blk", "his", "asn", "gender")
    labs <- c("Intercept", "Education", "Parents College",
                            "Age", "Race ID: Black", "Race ID: Hispanic",
                            "Race ID: Asian", "Gender ID: Woman")

@@

```{r}
    source(here("Functions", "pred.probs.R"))
    source(here("Functions", "plot.preds.R"))
    age.preds <- pred.probs(x = "age.n", res.latin$mods)
    p <- plot.preds(d = age.preds, 
                    xb = c(3, 7, 11),
                    xlabs = c("Young", "Mid. Aged", "Old"),
                    yl = .1, 
                    xm = 2, 
                    xl = 12)
    p
```
`

>>>>

```{r Custom Functions}
    source(here("Functions", "micro.genre.dat.R"))
    source(here("Functions", "demog.dat.R"))
    source(here("Functions", "genre.reg.mods.R"))
    source(here("Functions", "pred.probs.R"))
    source(here("Functions", "plot.preds.R"))
```

```{r}
    a <- demog.dat()
    summary(a)
    spec <- c("educ", "parcoll", "age.n", "blk", "his", "asn", "gender")
    labs <- c("Intercept", "Education", "Parents College",
                            "Age", "Race ID: Black", "Race ID: Hispanic",
                            "Race ID: Asian", "Gender ID: Woman")

@@

```{r}

    age.preds <- pred.probs(x = "age.n", res.latin$mods)
    p <- plot.preds(d = age.preds, 
                    xb = c(3, 7, 11),
                    xlabs = c("Young", "Mid. Aged", "Old"),
                    yl = .1, 
                    xm = 2, 
                    xl = 12)
    p
```
`
